Formal Verification of Real-Time Data Processing of the LHC Beam Loss Monitoring System: A Case Study

### 2011-03-22 fmics/paper.tex
Add citations for all those theorem provers
This is probably excessive...

HOL4 is an \emph{interactive} theorem prover: the user provides the high level proof strategy by composing functions that automate common chains of logical deduction.
The work described here could have been done using other systems such as HOL Light [ref], Isabelle/HOL~\cite{Isabelle}, ProofPower [ref], PVS [ref] or Coq [ref].
The first three of these support essentially the same version of higher-order logic as HOL4, whilst PVS and Coq support more powerful logics.
<What about ACL2?>
While offering less ``push-button'' automation than many other kinds of formal verification such as model-checking, machine-assisted theorem proving is the most appropriate approach to verifying the SRS, since it is unlikely that the correctness theorems, which need lemmas proved by manually guided mathematical induction, could be generated automatically.

>>>>

HOL4 is an \emph{interactive} theorem prover: the user provides the high level proof strategy by composing functions that automate common chains of logical deduction.
The work described here could have been done using other systems such as HOL Light~\cite{HOLLight,DBLP:conf/tphol/Harrison09a}, Isabelle/HOL~\cite{Isabelle}, ProofPower~\cite{ProofPower}, PVS~\cite{PVS,DBLP:conf/tphol/OwreS08} or Coq~\cite{Coq}.
The first three use essentially the same higher-order logic as HOL4, whilst PVS and Coq support more powerful logics.
<What about ACL2?>
While offering less ``push-button'' automation than other kinds of formal verification such as model-checking, machine-assisted theorem proving is appropriate for verifying the SRS, since it is unlikely that the correctness theorems, which need lemmas proved by manually guided mathematical induction, could be generated automatically.
